My title

### 2023-03-13 outputs/paper/paper.qmd
Added our Github repo link to the beginning of "paper.qmd" file.

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sakura Ariga
  - Aliyah Maxine Ramos
  - Annie Yan
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-educandinternet
#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
#| echo: false
## Highest Education Obtained VS. Internet Hours ##
mean_edu<- cleaned_2016gss_data %>%
  select(degree, wwwhr) %>%
  group_by(degree)%>%
  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
  pivot_wider(names_from = "degree", values_from = c("Mean_total"))

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sakura Ariga
  - Aliyah Maxine Ramos
  - Annie Yan
thanks: "Code and data are available at: https://github.com/AnnieYan0807/GSS-data-analysis.git."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

```{r}
#| label: fig-degreeandinternet
#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
#| echo: false
## Highest Education Obtained VS. Internet Hours ##
mean_edu<- cleaned_2016gss_data %>%
  select(degree, wwwhr) %>%
  group_by(degree)%>%
  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
  pivot_wider(names_from = "degree", values_from = c("Mean_total"))
